---
title: "Hooking Mortality"
author: "TBD"
output:
  html_document:
    fig_caption: yes
    theme: cerulean
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

***

Page Last Updated: `r format(Sys.time(), '%m/%d/%Y')`.

***


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Functions
```{r load functions, results = "hide",echo = T, message = FALSE, warning = FALSE}
wd_functions<-"functions"
sapply(FUN = source, paste(wd_functions, list.files(wd_functions), sep="/"))
```

# Install & Load Packages
This section of code will load the packages we need to complete the analysis
```{r load packages, results = "hide",echo = T, message = FALSE, warning = FALSE}
packages_list<-c("tidyverse", "plyr","dplyr", "lubridate","tidyr","scales","RODBC","MuMIn","RColorBrewer","reshape2","ggplot2","gplots","mgcv","sjPlot","sjmisc","gridExtra","modelr","kableExtra","dataRetrieval","MASS","brms","rstan","sf","riverdist","maptools","rgdal","raster","rgeos") 
install_or_load_pack(pack = packages_list)
```


# Read and organize data
```{r load data, results = "hide",echo = T, message = FALSE, warning = FALSE }
#locations from table
location.df<-odbc(accdb.name="CowlitzHookingMortalityDB.accdb",db.dir=getwd(),dsn="MS Access Database", sqtable="Location Index", fields= "*")%>%
  as_tibble()%>%
  mutate(lat=ifelse(!is.na(Loc_Lat),Loc_Lat,(US_Lat + DS_Lat)/2),
         lon=ifelse(!is.na(Loc_Lon),Loc_Lon,(US_Lon + DS_Lon)/2)
         )%>%
  filter(!is.na(lat))%>%
  dplyr::select(`Location Name`,lat,lon)

points.dec = SpatialPoints(cbind(location.df$lon, location.df$lat), proj4string=CRS("+proj=longlat"))

#cowlitz flow line shape file
river.sh<-st_read("WA_Hydrography_-_NHD_Flowline/WA_Hydrography_-_NHD_Flowline.shp")
points.plot <- data.frame(spTransform(points.dec, crs(river.sh)))%>%
  dplyr::rename(lon=coords.x1,lat=coords.x2)

#Map river with locations
ggplot() + 
  geom_sf(data = river.sh, size = 1, color = "black", fill = "cyan1") + 
  ggtitle("Cowlitz River & Hooking Mortality Study Locations") + 
  coord_sf()+
  geom_point(data=points.plot,mapping=aes(x=lon,y=lat),color="red",size=2)

river_sp<-readShapeLines(
  fn="WA_Hydrography_-_NHD_Flowline/WA_Hydrography_-_NHD_Flowline.shp",
  proj4string=CRS("+proj=merc +a=6378137 +b=6378137 +lat_ts=0 +lon_0=0 +x_0=0 +y_0=0 +k=1 +units=m +nadgrids=@null +wktext +no_defs ")
  , verbose=FALSE
  ,repair=FALSE
  ,delete_null_obj=FALSE
  )

river<-line2network(
  sp = river_sp,
  path = ".",
  layer = NA,
  tolerance = 100,
  reproject = NULL,
  supplyprojection = NULL
)

river_2<-setmouth(seg=354, vert=1, rivers=river)
#showends(seg=354,rivers=river)


points.UTM <- spTransform(points.dec, crs(river_sp))
points<-xy2segvert(x=points.UTM$coords.x1,y=points.UTM$coords.x2,rivers=river_2)

#plot(river)
#riverpoints(seg=points$seg, vert=points$vert, rivers=river, pch=15,col="blue")

RKM<-mouthdistbysurvey(
  unique=1:dim(points)[1],
  survey=rep(1,dim(points)[1]),
  seg=points$seg,
  vert=points$vert,
  rivers = river_2,
  logical = NULL,
  stopiferror = TRUE,
  algorithm = NULL
)/1000

location.df<-location.df%>%
  bind_cols(RKM=RKM)


# all captures
capture.df<-odbc(accdb.name="CowlitzHookingMortalityDB.accdb",db.dir=getwd(),dsn="MS Access Database", sqtable="All Captures Query", fields= "*")%>%
  as_tibble()%>%
  mutate(
    Year = as.numeric(year(ymd(as.character(Survey_Date)))),
    Month = as.numeric(month(ymd(as.character(Survey_Date)))),
    jdate = as.numeric(julian(ymd(as.character(Survey_Date)))),
    DOY = as.numeric(yday(ymd(as.character(Survey_Date)))),
    Capture_Type = ifelse(Capcode=="0", "No_Captures",
                                 ifelse(Capcode=="1", "New_Fish",
                                    ifelse(Capcode=="2", "Recapture",
                                      ifelse(Capcode=="3", "Natural_Origin",
                                        ifelse(Capcode=="5", "New_Fish","Lost"))))), #all variants of Capcode 4 were lost (we may want to differentiate for some analyses)
     #define initial capture as a control or treatment
    Treatment = ifelse(Survey_type%in%c("Control Release TP","Control Release MHE","Control Recycle"), "Control",
                                ifelse(Survey_type=="Angling", "Treatment","Other")),
    run_year = as.numeric(ifelse(as.numeric(Year=="2017")&as.numeric(Month>8)&SpeciesCode=="COHO","2017",
                               ifelse(as.numeric(Year=="2018")&as.numeric(Month<5)&SpeciesCode=="COHO","2017",
                                      ifelse(as.numeric(Year=="2018")&as.numeric(Month>8)&SpeciesCode=="COHO","2018",
                                             ifelse(as.numeric(Year=="2019")&as.numeric(Month<5)&SpeciesCode=="COHO","2018",
                                                    ifelse(as.numeric(Year=="2019")&as.numeric(Month>8)&SpeciesCode=="COHO","2019",
                                                           ifelse(as.numeric(Year=="2020")&as.numeric(Month<5)&SpeciesCode=="COHO","2019",
                                                                  ifelse(as.numeric(Year=="2017")&SpeciesCode=="STLHD","2017",
                                                                         ifelse(as.numeric(Year=="2018")&SpeciesCode=="STLHD","2018",
                                                                                ifelse(as.numeric(Year=="2019")&SpeciesCode=="STLHD","2019",
                                                                                       ifelse(as.numeric(Year=="2020")&as.numeric(Month<2)&SpeciesCode=="STLHD","2019",
                                                                                              ifelse(as.numeric(Year=="2020")&as.numeric(Month>2)&SpeciesCode=="STLHD","2020",as.numeric(Year))))))))))))
  ))%>%left_join(location.df,by=c(Release_Location="Location Name"))
  
#only first captures that were new fish (T or C)
firstcapture = capture.df%>%
  filter(Capcode=="1"|Capcode =="5") #these are initial captures and excludes Capcode 3s and 4s

#only first recaptures
recapture = capture.df%>%
  filter(Capcode=="2")%>%
  group_by(Fish_ID)%>%
  arrange(Survey_Date,TimeCapture)%>%
  slice(1L) #get first data/time recapure for each fish ID
  
#merge capture-recapture & create dummy variable for recaptures
dat<-firstcapture%>%
  left_join(recapture, by="Fish_ID",suffix=c("_cap","_recap"))%>%
  mutate(rec=ifelse(!is.na(DOY_recap),1,0))#join first captures with first recaptures
```
# NOTES 

### Analysis

Options for Analysis:
1. Binomial-logit with dummy variable with dummy variable for TC
2. Split binomial R2R
3. Time to recovery (survival analysis)

Things to explore in analysis
1. Including Capcode as a factor variable in the treatment effects would test for an "unaccounted for" control effect; Cap-code 5 would be lower recovery rate if unaccounted effect.


### Notes on Data and Database:
1. Added lat/long to database for Barrier Dam (missing originally)
2. Maybe need to exclude control Capcode 2 and 5's that were released in upper basin/brood first? 1 present in coho, several spring Chinook.

* Capcodes really important
  * Filter out capcode 0’s
  * Filter out wild fish
  * Capcode 5 = fish that went from control release to treatment fish
    * Initially tags pulled and new floys put in fish
    *	Later, fish simply release with old floys
* Multiple recap fish
  * Make sure to filter for initial releases and only “count” single recapture
* Consider removint fish that aren’t available for recapture
  * Capcode 1---look for “loss on capture” (mortality) in both treatments and controls
  * (only 5 controls died)
* Look for errata
  * Example: fish that had no release record but were recovered, we created a release record



# GAM analysis of factors affecting prob of recapture for control Coho
```{r GAM analysis Coho, results="hold",echo = T, message = T, warning = FALSE }
cdat<-dat%>%
  filter(SpeciesCode_cap=="COHO" & Treatment_cap=="Control")%>%
  dplyr::select(
    rec,
    Fish_ID,
    run_year_cap,
    DOY_cap,
    Temp_C_cap,
    Release_Location_cap,
    Capture_Location_recap,
    survey_ID_cap
                )%>%
  mutate(run_year_cap = factor(run_year_cap))

m1<-gam(rec ~ 
          1
          + s(run_year_cap,bs="re") 
          + s(DOY_cap,by=run_year_cap,k=20,m=1)
          + s(survey_ID_cap,bs="re",m=1)
          ,family = binomial(link="logit")
          ,data=cdat
    )

cat("\\begin{verbatim}")
cat(print("Summary GAM results for probability of recapture for control coho"))
try(cat(print(summary(m1)),silent = T))
cat(print("GAM Goodness of Fit check for probability of recapture for control coho"))
try(cat(print(gam.check(m1)),silent = T))
cat("\\end{verbatim}")


newdat<-expand.grid(
  DOY_cap = seq(from=min(cdat$DOY_cap),to=max(cdat$DOY_cap)),
  run_year_cap = unique(cdat$run_year_cap),
  survey_ID_cap = 0
  )%>%
  as_tibble()

preds=data.frame(preds=predict(newdata=newdat,m1,var="preds",type = "response", exclude = '(survey_ID_cap,bs="re",m=1)'))%>%
  as_tibble()

newdat<-newdat%>%
  bind_cols(preds)

ggplot(newdat,aes(x=DOY_cap,y=preds,color=run_year_cap))+
  geom_line(size=0.8)+
  ylim(0,1)+
  ylab("Predicted Probability of Recapture")+
  theme_bw()
```

# GAM analysis of factors affecting prob of recapture for Summer Steelhead
```{r GAM analysis S Steelhead, results="hold",echo = T, message = T, warning = FALSE }
cdat<-dat%>%
  filter(SpeciesCode_cap=="STLHD" & Treatment_cap=="Control")%>%
  dplyr::select(
    rec,
    Fish_ID,
    run_year_cap,
    DOY_cap,
    Temp_C_cap,
    Release_Location_cap,
    RKM_cap,
    Capture_Location_recap,
    survey_ID_cap
                )%>%
  mutate(run_year_cap = factor(run_year_cap))

m1<-gam(rec ~ 
          1
          + s(run_year_cap,bs="re") 
          + s(DOY_cap,by=run_year_cap,bs="ps",k=5,m=1)
          + s(RKM_cap,by=run_year_cap,bs="ps",k=3,m=1)
          + ti(RKM_cap,DOY_cap,by=run_year_cap,bs="ps",k=4)
          + s(survey_ID_cap,bs="re",m=1) 
          + RKM_cap
          ,family = binomial(link="logit")
          ,data=cdat
    )

cat("\\begin{verbatim}")
cat(print("Summary GAM results for probability of recapture for control coho"))
try(cat(print(summary(m1)),silent = T))
cat(print("GAM Goodness of Fit check for probability of recapture for control coho"))
try(cat(print(gam.check(m1)),silent = T))
cat("\\end{verbatim}")


newdat<-expand.grid(
  DOY_cap = seq(from=min(cdat$DOY_cap),to=max(cdat$DOY_cap)),
  run_year_cap = unique(cdat$run_year_cap),
  RKM_cap = unique(cdat$RKM_cap),
  survey_ID_cap = 0
  )%>%
  as_tibble()

preds=data.frame(preds=predict(newdata=newdat,m1,var="preds",type = "response", exclude = '(survey_ID_cap,bs="re",m=1)'))%>%
  as_tibble()

newdat<-newdat%>%
  bind_cols(preds)


ggplot(newdat,aes(x=DOY_cap,y=preds,color=factor(RKM_cap)))+
  geom_line(size=0.8)+
  facet_wrap(~run_year_cap,ncol=1)+
  ylim(0,1)+
  ylab("Predicted Probability of Recapture")+
  theme_bw()
```
# GAM analysis of factors affecting prob of recapture for Winter Steelhead

NOTE: analysis NOT final...still lack of fit for tensor product interaction term...need to examine residuals...steelhead data funky as expected...possibly filter recovery locations to separator.
```{r GAM analysis W Steelhead, results="hold",echo = T, message = T, warning = FALSE }
cdat<-dat%>%
  filter(SpeciesCode_cap=="WSTLHD" & Treatment_cap=="Control")%>%
  dplyr::select(
    rec,
    Fish_ID,
    run_year_cap,
    DOY_cap,
    Temp_C_cap,
    Release_Location_cap,
    RKM_cap,
    Capture_Location_recap,
    survey_ID_cap
                )%>%
  mutate(run_year_cap = factor(run_year_cap))

m1<-gam(rec ~ 
          1
          + s(run_year_cap,bs="re")
          + s(DOY_cap,by=run_year_cap,bs="ps",k=10,m=1)
          + s(RKM_cap,by=run_year_cap,bs="ps",k=3,m=1)
          + ti(RKM_cap,DOY_cap,by=run_year_cap,bs="ps",k=12,m=2)
          + s(survey_ID_cap,bs="re",m=1)
          + RKM_cap
          ,family = binomial(link="logit")
          ,data=cdat
    )

cat("\\begin{verbatim}")
cat(print("Summary GAM results for probability of recapture for control coho"))
try(cat(print(summary(m1)),silent = T))
cat(print("GAM Goodness of Fit check for probability of recapture for control coho"))
try(cat(print(gam.check(m1)),silent = T))
cat("\\end{verbatim}")


newdat<-expand.grid(
  DOY_cap = seq(from=min(cdat$DOY_cap),to=max(cdat$DOY_cap)),
  run_year_cap = unique(cdat$run_year_cap),
  RKM_cap = unique(cdat$RKM_cap),
  survey_ID_cap = 0
  )%>%
  as_tibble()

preds=data.frame(preds=predict(newdata=newdat,m1,var="preds",type = "response", exclude = '(survey_ID_cap,bs="re",m=1)'))%>%
  as_tibble()

newdat<-newdat%>%
  bind_cols(preds)


ggplot(newdat,aes(x=DOY_cap,y=preds,color=factor(RKM_cap)))+
  geom_line(size=0.8)+
  facet_wrap(~run_year_cap,ncol=1)+
  ylim(0,1)+
  ylab("Predicted Probability of Recapture")+
  theme_bw()
```

# GAM analysis of factors affecting prob of recapture for spring Chinook

ONLY use 2018 controls, exlcude all but barrier dam (which means this applies to angled fish too)
```{r GAM analysis SPCK, results="hold",echo = T, message = T, warning = FALSE }
cdat<-dat%>%
  filter(SpeciesCode_cap=="SCHK" & Treatment_cap=="Control" & Release_Location_cap == "Barrier Dam Launch")%>%
  dplyr::select(
    rec,
    Fish_ID,
    run_year_cap,
    DOY_cap,
    Temp_C_cap,
    Release_Location_cap,
    RKM_cap,
    Capture_Location_recap,
    survey_ID_cap
                )%>%
  mutate(run_year_cap = factor(run_year_cap))

m1<-gam(rec ~ 
          1
          #+ s(run_year_cap,bs="re")
          + s(DOY_cap,bs="ps",k=10,m=1)
          #+ s(RKM_cap,by=run_year_cap,bs="ps",k=3,m=1)
          #+ ti(RKM_cap,DOY_cap,by=run_year_cap,bs="ps",k=12,m=2)
          + s(survey_ID_cap,bs="re",m=1)
          #+ RKM_cap
          ,family = binomial(link="logit")
          ,data=cdat
    )

cat("\\begin{verbatim}")
cat(print("Summary GAM results for probability of recapture for control coho"))
try(cat(print(summary(m1)),silent = T))
cat(print("GAM Goodness of Fit check for probability of recapture for control coho"))
try(cat(print(gam.check(m1)),silent = T))
cat("\\end{verbatim}")


newdat<-expand.grid(
  DOY_cap = seq(from=min(cdat$DOY_cap),to=max(cdat$DOY_cap)),
  run_year_cap = unique(cdat$run_year_cap),
  RKM_cap = unique(cdat$RKM_cap),
  survey_ID_cap = 0
  )%>%
  as_tibble()

preds=data.frame(preds=predict(newdata=newdat,m1,var="preds",type = "response", exclude = '(survey_ID_cap,bs="re",m=1)'))%>%
  as_tibble()

newdat<-newdat%>%
  bind_cols(preds)


ggplot(newdat,aes(x=DOY_cap,y=preds,color=factor(RKM_cap)))+
  geom_line(size=0.8)+
  facet_wrap(~run_year_cap,ncol=1)+
  ylim(0,1)+
  ylab("Predicted Probability of Recapture")+
  theme_bw()
```

# Simulation GLM for dummy variable survival analysis
```{r simulated data model check, results="hold",echo = T, message = T, warning = FALSE }
n<-2000 #total fish
n_t=round(0.5*n) #number of treatment fish
TC<-data.frame(TC=c(rep(0,(n-n_t)),rep(1,n_t))) #dummy vector for Treatment and controls
k_rec<-3 #count of global covariates including global intercept
k_surv<-2 #count of global covariates
b<-rnorm(k_rec+k_surv,0,1) # beta's for global covariates
x<-bind_cols(data.frame("int"=rep(1,n)),as_tibble(mvrnorm(n=n,mu=rep(0,k_rec+k_surv-1), Sigma=diag(k_rec+k_surv-1)))) #design matrix


#=========
# binomial
#=========
logit_pred<-data.frame(logit_pred=as.matrix(x[,1:k_rec]) %*% b[1:k_rec] + #global covariates and intercept
    as.matrix((as.matrix(x[,(k_rec+1):(k_rec+k_surv)]) * cbind(TC,TC))) %*% b[(k_rec+1):(k_rec+k_surv)]) #treatment covariates (interaction with dummy variable)

#=========
# R2R
#=========
logit_pred<-data.frame(logit_pred=logit(ilogit(as.matrix(x[,1:k_rec]) %*% b[1:k_rec] + #global covariates and intercept
                                               as.matrix((as.matrix(x[,(k_rec+1):(k_rec+k_surv)]) * cbind(TC,TC))) %*% b[(k_rec+1):(k_rec+k_surv)]))) #treatment covariates (interaction with dummy variable)

dat<-x%>%
  bind_cols(TC)%>%
  bind_cols(logit_pred)%>%
  as_tibble()%>%
  mutate(
  rec = rbinom(n=n, size=1, prob= ilogit(logit_pred))
  )


#==========
# BRMS fits
#==========
fmla<-as.formula(paste0("rec ~ ",paste("V",1:(k_rec-1),sep="",collapse =   "+ "),"+", paste("TC : V",(k_rec):(k_rec+k_surv-1),sep="",collapse =   "+ ")))

#m1<-brm(fmla, family = bernoulli(link="logit"),data=dat,cores = 4,chains=4,iter=2000,warmup = 1000)
#m1<-brm(fmla, family = poisson(link="log"),data=dat,cores = 4,chains=4,iter=2000,warmup = 1000)
m1<-glm(fmla, family = binomial(link="logit"),data=dat)

cat("\\begin{verbatim}")
cat(print("Summary GLM results with simulated data"))
try(cat(print(summary(m1)),silent = T))
cat(print("Actual parameter values used to generate simulated data"))
print(b)
cat("\\end{verbatim}")
```

# A stan model for fitting R2R models with no covariates
```{r }
processFile(file.path("stan_models", "R2R.stan"))
```



